---
title: "Trophic cascades and fisheries"
rtitle: "Trophic cascades"
author: "Juan Carlos Villaseñor-Derbez$^{*1}$"
institution: "$^1$Bren School, UCSB"
email: "jvillasenor@bren.ucsb.edu"
abstract: "Fishing can change the whole system"
keywords: "Fish, Fisheries, Trophic"
corrauth: "Something"
output:
  bookdown::pdf_document2:
    template: template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width = 5, fig.height = 3)
```

# Introduction

Marine reserves can yield benefits to tourism \citep{viana_2017}. People have looked at the ideal size of TURFs \citep{acevesbueno_2017}. Also, \citet{szuwalski_2017} showed that reducing predator abundances can increase catches of lower--trophic level fish.

# Materials and methods

We will use a two-species predator-prey model, described by:


\begin{equation}
\begin{split} \label{eq:pred_prey}
\frac{dN}{dt} = r N - a N P \\	 
\frac{dP}{dt} = c a N P - m P -fP
\end{split}
\end{equation}

```{r}
suppressPackageStartupMessages({
  library(knitr)
  library(deSolve)
  library(cowplot)
  library(tidyverse)
})
```

```{r}
# Define parameters
r <- 1
a <- 1
c <- 0.1
m <- 0.1
f <- 0

params <- c(r, a, c, m, f)

# Define initial conditions
A0 <- 1
S0 <- 2

values <- c(A0, S0)

# Time
t <- seq(0, 100)

```


```{r}
predator_prey <- function(t, values, params){
  # Extract parameters
  r <- params[1]
  a <- params[2]
  c <- params[3]
  m <- params[4]
  f <- params[5]

  # Extract state variables
  A <- values[1]
  S <- values[2]
  
  dAdt <- (r*A) - (a*A*S)
  dSdt <- (a*c*A*S) - (m*S) - (f*S)
  
  return(list(c(dAdt, dSdt)))
}
```

```{r}
no_fishing <- deSolve::lsoda(y = values, times = t, func = predator_prey, parms = params) %>% 
  as.data.frame() %>% 
  magrittr::set_colnames(value = c("Time", "Anchovies", "Sharks")) %>% 
  gather(Species, Abundance, -Time) %>% 
  mutate(Model = "No Fishing")
```

```{r}
plot_no_fish <- ggplot(no_fishing, aes(x = Time, y = Abundance, color = Species)) +
  geom_line(size = 1) +
  scale_color_brewer(palette = "Set1")
```


```{r}
f <- 0.1
params <- c(r, a, c, m, f)

fishing <- deSolve::lsoda(y = values, times = t, func = predator_prey, parms = params) %>% 
  as.data.frame() %>% 
  magrittr::set_colnames(value = c("Time", "Anchovies", "Sharks")) %>% 
  gather(Species, Abundance, -Time) %>% 
  mutate(Model = "Fishing")
```

```{r}
plot_fish <- ggplot(fishing, aes(x = Time, y = Abundance, color = Species)) +
  geom_line(size = 1) +
  scale_color_brewer(palette = "Set1")
```

\clearpage

# Results

Using Equation \ref{eq:pred_prey} we obtain the dynamics of the system, shown in Figure \ref{fig:timeseries}. The stable equilibrium values are shown in Table \ref{tab:stable_eq}.

```{r, fig.height = 5, fig.cap = "\\label{fig:timeseries}State variabel dynamics through time for an ecosystem without fishing (A) and with fishing (B)."}
plot_grid(plot_no_fish, plot_fish, ncol = 1, labels = "AUTO")
```

```{r}
rbind(no_fishing, fishing) %>% 
  filter(Time == 100) %>% 
  spread(Model, Abundance) %>% 
  select(-Time) %>% 
  knitr::kable(digits = 2, caption = "\\label{tab:stable_eq}Stable equilibrium values for Sharks and Anchovies under fishing and no fishing conditions") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```


# Discusion and Conclusion

Our results are not novel, because they had been shown before \citep{szuwalski_2017}.

\clearpage

\bibliographystyle{frontiersinSCNS_ENG_HUMS}
\bibliography{references}