---
title: "Lotka-Volterra system and fisheries"
author: "Juan Carlos Villaseñor-Derbez"
institution: "Bren, UCSB"
corrauth: "Bren Hall, 2400 UCSB"
email: "jvillasenor@bren.ucsb.edu"
abstract: "kzhbgvadjhtbdkgtkj"
keywords: "Keyword1, Keyword2"
output:
  bookdown::pdf_document2:
    template: template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Marine reserves can help tourism \citep{viana_2017}. Pero \citet{acevesbueno_2017} dice que el tamaño del TURF importa. \citet{costello2016} dice que arreglemos las pesquerias.

\begin{equation}
a = b
\end{equation}

# Materials and Methods

We use Eq \ref{eq:slope_inter} to run our analysis.

\begin{equation}
y = mx + b
\label{eq:slope_inter}
\end{equation}

# Results

We use Eq \ref{eq:slope_inter} to get Figure \ref{fig:plot_hist}.

```{r}
suppressPackageStartupMessages({
  library(cowplot)
  library(ggplot2)
})
```

```{r, fig.width = 6, fig.height = 6, fig.cap = "\\label{fig:plot_hist}Displacement as a function of hp (a), and a histogram of displacement (b)"}
plot1 <- ggplot(data = mtcars, aes(x = disp, y = hp, color = cyl)) +
  geom_point()

plot2 <- ggplot(data = mtcars, aes(x = disp)) +
  geom_histogram(binwidth = 20)

plot_grid(plot1, plot2, nrow = 2, labels = "auto")
```



# Discusion and Conclusion

\bibliographystyle{frontiersinSCNS_ENG_HUMS}
\bibliography{references}









