---
title: "Notes"
author: "Juan Carlos Villaseñor-Derbez"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# During presentation

- Explain Rmd

- Explain differential equations

# Live-coding

## Basic Rmd file

- Open an Rmarkdown document
- Title vs. file name
- Explain how to choose type of output
- Explain the default Rmd file (setup chunk)
- Tips about options in the engine icon
- `Knit` so they see how it ends up

## Modificatios to default

- Delete all, include the typical sections of a paper

- To get the `LaTeX` template working:
    - Show them the LaTeX template, and some of the metadata that needs to go in the `YAML`
    - Set output type in the `YAML`, specifying output format and template to use:
    - Add `rtitle`, `institution`, `email`, `abstract`, `keywords`, `corrauth`, it should look like this:

```
---
title: "Trophic cascades and fisheries"
rtitle: "Trophic cascades"
author: "Juan Carlos Villaseñor-Derbez$^{*1}$"
institution: "$^1$Bren School, UCSB"
email: "jvillasenor@bren.ucsb.edu"
abstract: "Fishing can change the whole system"
keywords: "Fish, Fisheries, Trophic"
corrauth: "Something"
date: "16 de febrero de 2018"
output:
  bookdown::pdf_document2:
    template: template.tex
---
```
    - Set `echo = F`, `fig.height` and `fig.width` in the setup chunk
    - `Knit` the document


## Citations

- To include references:
    - Explain what the reference style file is ([Styles here](http://editor.citationstyles.org/about/))
    - Explain what a `BibTex` file is:
        - show them how to get it from F1000Workspace
        - and GoogleScholar
    - At the bottom of the file, include
        - `\bibliographystyle{frontiersinSCNS_ENG_HUMS}`
        - and `\bibliography{references}`
- Cite with parentheses `\citep{}`
    - `Knit`
- Cite without parenthesees `\citet{}`
    - `Knit`

## Equations

- Explain `\begin{split}`
- Explain `\frac{}{}`
- First with `$$ equation $$`
- Replace the `$$` with `\begin{equation}
- Use `\label{eq:pred_prey}`

```
\begin{equation}
\begin{split} \label{eq:pred_prey}
\frac{dA}{dt} = I_A - d_AA - aAS \\
\frac{dS}{dt} = ar_SAS - d_SS -fS
\end{split}
\end{equation}
```
\begin{equation}
\begin{split} \label{eq:pred_prey}
\frac{dA}{dt} = I_A - d_AA - aAS \\
\frac{dS}{dt} = ar_SAS - d_SS -fS
\end{split}
\end{equation}

## Load packages

- Show them how to suppress package messages with `suppressPackageStartupMessages({})`
- Explain what each package does:
    - `library(knitr)`
    - `library(deSolve)`
    - `library(cowplot)`
    - `library(tidyverse)`
    
## Running the model

- We will have two scenarios:
    - a) no fishing effort, pristine seas
    - b) fishing effort, real world

- Explain what `lsoda` needs to motivate the next sections of code
    - needs three vectors and a function:
        - `y`: Initial conditions
        - `times`: Places where we want to have values solved
        - `params`: The parameters
        - `func`: A function that contains the system
    
- Define the parameters for scenario a

```{r, eval = F}
# Define parameters
Ia <- 10
da <- 0.2
a <- 0.01
rs <- 0.5
ds <- 0.1
f <- 0

params <- c(Ia, da, a, rs, ds, f)

# Define initial conditions
A0 <- 2
S0 <- 2

values <- c(A0, S0)

# Time
t <- seq(0, 100)
```

- Define the function that has the form of the equation above

```{r, eval = F}
predator_prey <- function(t, values, params){
  # Extract parameters
  Ia <- params[1]
  da <- params[2]
  a <- params[3]
  rs <- params[4]
  ds <- params[5]
  f <- params[6]
  
  # Extract state variables
  A <- values[1]
  S <- values[2]
  
  dAdt <- Ia - (da*A) - (a*A*S)
  dSdt <- (a*rs*A*S) - (ds*S) - (f*S)
  
  return(list(c(dAdt, dSdt)))
}
```

- Show how to use `deSolve::lsoda` and step by step add code that makes it look better

```{r, eval = F}
no_fishing <- deSolve::lsoda(y = values, times = t, func = predator_prey, parms = params) %>% 
  as.data.frame() %>% 
  magrittr::set_colnames(value = c("Time", "Anchovies", "Sharks")) %>% 
  gather(Species, Abundance, -Time) %>% 
  mutate(Model = "No Fishing")
```

- Show them how to plot, first without assigning the plot to a value

```{r, eval = F}
ggplot(no_fishing, aes(x = Time, y = Abundance, color = Species)) +
  geom_line(size = 1) +
  scale_color_brewer(palette = "Set1")
```

- Repeat but with fishing effor this time

```{r, eval = F}
f <- 0.05
params <- c(Ia, da, a, rs, ds, f)

fishing <- deSolve::lsoda(y = values, times = t, func = predator_prey, parms = params) %>% 
  as.data.frame() %>% 
  magrittr::set_colnames(value = c("Time", "Anchovies", "Sharks")) %>% 
  gather(Species, Abundance, -Time) %>% 
  mutate(Model = "Fishing")
```

 - And plot it
 
```{r, eval = F}
gplot(fishing, aes(x = Time, y = Abundance, color = Species)) +
  geom_line(size = 1) +
  scale_color_brewer(palette = "Set1")
```

> But wait! Plots are not meant to be on the Methods section... And they would look way better together too.

## Reults section

- A results section will have a figure and a table, and text that references these

- Write a couple sentences tha refeence the equation.

- `cowplot`
    - Assign the previous plots to `plot_no_fishing` and `plot_fishing`
    - Run basic cowplot
```{r, eval = F}
cowplot::plot_grid(plot_no_fish, plot_fish, ncol = 1, labels = "AUTO")
```
    - Add figure details:
        - `fig.height = 5`
        - `fig.cap = "\\label{fig:timeseries}State variabel dynamics through time for an ecosystem without fishing (A) and with fishing (B)."`

- Write sentence that references the figure

- Create a table of stable equilibrium
    - `rbind` the two dataframes
    - Step by step, show how to `filter` to keep only the last values
    - `spread` to get the table(ish) we want
    - `select` to get rid of the `Time` column
    - `knitr` package to creat a table
        - `caption` that inludes a label to the table
    - Sentence that references the table
    - `Knit` to show the table is ugly
    - Enter `kableExtra` to show them how to modify position

```{r, eval = F}
rbind(no_fishing, fishing) %>% 
  filter(Time == 100) %>% 
  spread(Model, Abundance) %>% 
  select(-Time) %>% 
  knitr::kable(digits = 2, caption = "\\label{tab:stable_eq}Stable equilibrium values for Sharks and Anchovies under fishing and no fishing conditions") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```









