---
title: "Section 1 - Exercise 1"
author: "Juan Carlos Villaseñor-Derbez"
date: "24 de enero de 2018"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    toc_scroll: smooth
---

# Logistic growth model

## a

Write a logistic population growth model

$$
N_t = N_{t-1} + gN_{t-1}\left(1-\frac{N_{t-1}}{K}\right) -fN_{t-1}
$$

### Define parameters

```{r}
g <- 0.5 # growth rate
K <- 100 # carrying capacity
f <- 0.3 # fishing mortality

time = c(1:50) # vector with times
N <- rep(NA, length = length(t)) # vector (with NAs) with the same length as times
N[1] <- 50 # define population at time t = 1
```

### Simulate population growth

```{r}
# For loop that iterates over time
for(t in 2:max(time)){
  N[t] <- N[t-1] + (g*N[t-1]*(1-(N[t-1]/K))) - f*N[t-1]
}
```

### Tasks

### 1) Plot population size over time

```{r, fig.cap = "Population size over time"}
suppressPackageStartupMessages(library(tidyverse))

data.frame(time, population = N) %>% 
  ggplot(aes(x = time, y = population)) +
  geom_line() +
  geom_point(color = "steelblue", size = 2) +
  theme_classic()
```

#### 2) Plot yield over time

```{r, "Yield over time"}
data.frame(time, population = f*N) %>% 
  ggplot(aes(x = time, y = population)) +
  geom_line() +
  geom_point(color = "steelblue", size = 2) +
  theme_classic()
```

### Questions

#### 1) What is the total yield in 50 years?

```{r}
yield <- sum(f*N)
```

>Total yield in 50 years is `r yield`.

#### 2) What is the yield and population size in year 50?

```{r}
yield_t50 <- f*N[50]
```

>Yield at $t = 50$ is `r yield_t50`

## b

Test differente values of fishing mortality $f$

### Tasks 

#### Define parameters

```{r}
g <- 0.5 # growth rate
K <- 100 # carrying capacity
f_vec <- seq(0, 1, by = 0.1) # vector of fishing mortalities

time = c(1:50) # vector with times
N <- matrix(NA, nrow = length(time), ncol = length(f_vec)) # matrix (with NAs) with nrow as times and ncol as f_vec
N[1, ] <- 50 # define population at time t = 1
```

#### Simulate population growth

```{r}
# for loop tha titerates over f_vec (do not confuse k with K)
for (k in 1:length(f_vec)){
  f <- f_vec[k] #define an f for this particular loop
  # For loop that iterates over time
  for(t in 2:max(time)){
    N[t, k] <- N[t-1, k] + (g*N[t-1, k]*(1-(N[t-1, k]/K))) - f*N[t-1, k]
  }
}
```

#### 1) Plot population size over time, for each fishing mortality

```{r}
data.frame(time, N) %>% 
  magrittr::set_colnames(c("time", paste("f = ", f_vec))) %>% 
  gather(fishing_mortality, population, -time) %>% 
  ggplot(aes(x = time, y = population, color = fishing_mortality, group = fishing_mortality)) +
  geom_line(color = "black") +
  geom_point() +
  theme_classic()
```

#### 2) Plot yield over time for each fishing mortality

```{r}
data.frame(time, N) %>% 
  magrittr::set_colnames(c("time", f_vec)) %>% 
  gather(f, N, -time) %>% 
  mutate(f = as.numeric(f),
         Yield = f * N,
         fishing_mortality = paste("f = ", formatC(f, digits = 0))) %>% 
  ggplot(aes(x = time, y = Yield, color = fishing_mortality, group = fishing_mortality)) +
  geom_line(color = "black") +
  geom_point() +
  theme_classic()
```

#### 3) Yield at year 50 for each fishing mortality

```{r}
data.frame(f = f_vec,
           yield_50 = f_vec * N[50, ],
           fishing_mortality = paste("f = ", formatC(f_vec, digits = 0))) %>% 
  ggplot(aes(x = fishing_mortality, y = yield_50, fill = f)) +
  geom_col() +
  theme_classic()
```

#### 4) Total yield for each fishing mortality

```{r}
data.frame(time, N) %>% 
  magrittr::set_colnames(c("time", f_vec)) %>% 
  gather(f, N, -time) %>% 
  mutate(f = as.numeric(f),
         Yield = f * N,
         fishing_mortality = paste("f = ", formatC(f, digits = 0))) %>% 
  group_by(f, fishing_mortality) %>% 
  summarize(Yield = sum(f * N)) %>% 
  ggplot(aes(x = fishing_mortality, y = Yield, fill = f)) +
  geom_col() +
  theme_classic()
```


### Questions

#### Which fishing mortality gives the largest total yield?

>$f = 0.3$ gives the largest yield

#### How does answer from 1) change if you model only 3 years? Why?


```{r}
g <- 0.5 # growth rate
K <- 100 # carrying capacity
f_vec <- seq(0, 1, by = 0.1) # vector of fishing mortalities

time = c(1:3) # vector with times
N <- matrix(NA, nrow = length(time), ncol = length(f_vec)) # matrix (with NAs) with nrow as times and ncol as f_vec
N[1, ] <- 50 # define population at time t = 1
```

```{r}
# for loop tha titerates over f_vec (do not confuse k with K)
for (k in 1:length(f_vec)){
  f <- f_vec[k] #define an f for this particular loop
  # For loop that iterates over time
  for(t in 2:max(time)){
    N[t, k] <- N[t-1, k] + (g*N[t-1, k]*(1-(N[t-1, k]/K))) - f*N[t-1, k]
  }
}
```

```{r}
data.frame(time, N) %>% 
  magrittr::set_colnames(c("time", f_vec)) %>% 
  gather(f, N, -time) %>% 
  mutate(f = as.numeric(f),
         Yield = f * N,
         fishing_mortality = paste("f = ", formatC(f, digits = 0))) %>% 
  group_by(f, fishing_mortality) %>% 
  summarize(Yield = sum(f * N)) %>% 
  ggplot(aes(x = fishing_mortality, y = Yield, fill = f)) +
  geom_col() +
  theme_classic()
```

>With a time horizon with 3 years, $f = 0.9$ gives the largest yield

#### Which fishing mortality gives you the highest equilibrium yield (t = 50)?

>$f = 0.3$ gives the largest yield at equilibrium

#### What happens to answer 3) if you change the growth rate to 0.2? Why?

```{r}
g <- 0.2 # growth rate
K <- 100 # carrying capacity
f_vec <- seq(0, 1, by = 0.1) # vector of fishing mortalities

time = c(1:50) # vector with times
N <- matrix(NA, nrow = length(time), ncol = length(f_vec)) # matrix (with NAs) with nrow as times and ncol as f_vec
N[1, ] <- 50 # define population at time t = 1
```

```{r}
# for loop tha titerates over f_vec (do not confuse k with K)
for (k in 1:length(f_vec)){
  f <- f_vec[k] #define an f for this particular loop
  # For loop that iterates over time
  for(t in 2:max(time)){
    N[t, k] <- N[t-1, k] + (g*N[t-1, k]*(1-(N[t-1, k]/K))) - f*N[t-1, k]
  }
}
```

```{r}
data.frame(f = f_vec,
           yield_50 = f_vec * N[50, ],
           fishing_mortality = paste("f = ", formatC(f_vec, digits = 0))) %>% 
  ggplot(aes(x = fishing_mortality, y = yield_50, fill = f)) +
  geom_col() +
  theme_classic()
```

>With $g = 0.2$, $f = 0.1$ gives the largest yield at equilibrium.

#### Why is the optimal fishing mortality lower than the growth rate?

>For population to persist, $f < g$






